A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-01 02_Materials_and_Methods.Rmd
producing some skeleton text for the materials and methods section

The resulting dataset **TODO**

- Spatial Distance

- Cultural distance

The SED is defined as:

@@

- Simulation

>>>>

The resulting dataset contains **TODO**

This data for individual graves attributed to a macroregion can be transformed to a timeseries of trait prevalence within the respective regions during the the timeframe of interest. The first step is to create a absolute occurence time series **TODO**

The continous timeseries of yearwise burial rite proportions for each region allow to calculate timeseries of a measure of cultural distance for each region relation (Figure **TODO**). Several different measures of cultural distance could be used here following the discussion of these matters in the relevant literature (**TODO**). In this context the Squared Euclidian Distance (SED) seems to be a sensible statistic, because it is fairly simple, works with only few assumptions and emphasizes differences through squaring.

The SED is defined here as:

@@

To test for correlation between the distances based on the variables *burial type* and *burial construction*, the timeframe of interest was devided into sections of 200 years. For each section of each the two variables, a matrix of the mean SED over time was calculated. The two matrizes of each section can be tested for correlation with the Mantel test, which **TODO**. The mean correlation for each of the $\frac{8*8}{2}-\frac{8}{2}=28$ region-region relations can be plotted in the *burial type*SED-*burial construction*SED space (Figure **TODO**).

Defining a measure of spatial distance for the above defined main units of observation, the macroregions, is only possible in a highly simplified way. A contionus distance measure can't be employed, but it's possible to distinguish ordinal distance classes. For the eight regions four different categories of spatial distance were defined.

Simulation **TODO**
